Enhancement of SDR in Thessaloniki

### 2024-02-19 GHI_enh_04_investigate.tex
Commit 2024-01-30 13:15
Commit 2024-01-31 14:13
Commit 2024-02-01 14:14
Commit 2024-02-08 13:10
Commit 2024-02-19 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-22}

@@

@@

lmD: 1.71458 +/- 0.1322584

lmY: 1.714601 +/- 0.1322612

Arima: 1.7152 0.1817 9.4404 0

@@

lmD: 1.015311 +/- 0.173386

lmY: 1.015342 +/- 0.1733898

Arima: 1.1004 0.255 4.3146 0

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

@@

Arima: -0.1679 3.8757 -0.0433 0.9654

@@

lmD: 605.1187 +/- 96.27827

lmY: 605.1308 +/- 96.28033

Arima: 605.7835 145.2351 4.1711 0

@@

lmD: 0.002984713 +/- 0.0002850018

lmY: 0.00298475 +/- 0.0002850079

Arima: 0.003 4e-04 7.7371 0

@@

lmD: 0.001565283 +/- 0.0003220401

lmY: 0.001565348 +/- 0.000322047

Arima: 0.0018 5e-04 3.3956 7e-04

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

@@

lmD: 0.9735636 +/- 0.1446246

lmY: 0.9735884 +/- 0.1446277

Arima: 1.0386 0.2143 4.8455 0

@@

lmD: 0.7131394 +/- 0.1236589

lmY: 0.7131522 +/- 0.1236614

Arima: 0.7132 0.1476 4.8325 0

@@

lmD: 0.1205603 +/- 0.04472432

lmY: 0.1205635 +/- 0.04472525

Arima: 0.1206 0.0487 2.4752 0.0133

@@

lmD: 0.5126011 +/- 0.05584138

lmY: 0.5126089 +/- 0.05584254

Arima: 0.5126 0.0703 7.2901 0

@@

lmD: 28.03241 +/- 3.452126

lmY: 28.0328 +/- 3.452198

Arima: 28.0362 4.3653 6.4225 0

@@

lmD: 0.001091243 +/- 0.0001452364

lmY: 0.001091258 +/- 0.0001452394

Arima: 0.0011 2e-04 6.6404 0

@@

lmD: 0.0002586606 +/- 6.142941e-05

lmY: 0.0002586644 +/- 6.143069e-05

Arima: 3e-04 1e-04 3.7461 2e-04

@@

lmD: 0.03561979 +/- 0.004001997

lmY: 0.03562032 +/- 0.004002081

Arima: 0.0356 0.0048 7.3697 0

@@

lmD: -0.1184401 +/- 0.3426654

lmY: -0.1183983 +/- 0.3426728

Arima: -0.1021 0.5303 -0.1925 0.8473

@@

lmD: -0.2498159 +/- 0.2873017

lmY: -0.2497925 +/- 0.287308

Arima: -0.249 0.4778 -0.5212 0.6022

@@

lmD: 0.02397815 +/- 0.02221734

lmY: 0.02397998 +/- 0.02221782

Arima: 0.024 0.0229 1.0454 0.2959

@@

lmD: 4.678815 +/- 4.938622

lmY: 4.679265 +/- 4.938728

Arima: 4.6804 5.0982 0.9181 0.3586

@@

lmD: 0.0002750923 +/- 0.0002421161

lmY: 0.0002751196 +/- 0.0002421213

Arima: 3e-04 3e-04 1.0722 0.2836

@@

lmD: 0.0001464247 +/- 0.0001495252

lmY: 0.0001464348 +/- 0.0001495284

Arima: 1e-04 2e-04 0.8844 0.3765

@@

lmD: 0.007036274 +/- 0.006116865

lmY: 0.007036819 +/- 0.006116997

Arima: 0.007 0.0063 1.1208 0.2624

@@

@@

\begin{verbatim}
2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-19}

@@

\begin{verbatim}
The following objects are masked from 'package:data.table':

    yearmon, yearqtr
\end{verbatim}

@@

lmD: 1.539332 +/- 0.1014749

lmY: 1.539352 +/- 0.1014768

Arima: 1.5397 0.1354 11.3752 0

@@

lmD: 1.077113 +/- 0.1694257

lmY: 1.077139 +/- 0.1694289

Arima: 1.1517 0.2512 4.5849 0

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

Arima: 0.2014 5.4204 0.0371 0.9704

@@

lmD: 499.2985 +/- 96.76248

lmY: 499.3033 +/- 96.76432

Arima: 500.4495 151.9546 3.2934 0.001

@@

lmD: 0.003568686 +/- 0.0002801799

lmY: 0.003568727 +/- 0.0002801853

Arima: 0.0036 4e-04 9.731 0

@@

lmD: 0.001823537 +/- 0.0003202326

lmY: 0.00182361 +/- 0.0003202387

Arima: 0.002 5e-04 3.8775 1e-04

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

lmD: 0.9626897 +/- 0.1495875

lmY: 0.9627106 +/- 0.1495904

Arima: 1.0336 0.2275 4.5431 0

@@

lmD: 0.8351144 +/- 0.09713712

lmY: 0.8351303 +/- 0.09713899

Arima: 0.8351 0.1135 7.3608 0

@@

lmD: 0.163156 +/- 0.03446857

lmY: 0.1631591 +/- 0.03446923

Arima: 0.1632 0.0372 4.3911 0

@@

lmD: 0.5453637 +/- 0.04850372

lmY: 0.5453737 +/- 0.04850466

Arima: 0.5454 0.0575 9.4902 0

@@

lmD: 26.14448 +/- 2.49671

lmY: 26.145 +/- 2.496759

Arima: 26.1448 3.0029 8.7066 0

@@

lmD: 0.001478147 +/- 0.0001452906

lmY: 0.001478168 +/- 0.0001452934

Arima: 0.0015 2e-04 8.804 0

@@

lmD: 0.0003397602 +/- 6.739233e-05

lmY: 0.0003397619 +/- 6.739364e-05

Arima: 3e-04 1e-04 4.6072 0

@@

lmD: 0.04427476 +/- 0.004265004

lmY: 0.04427565 +/- 0.004265086

Arima: 0.0443 0.0049 9.0734 0

@@

lmD: 0.239157 +/- 0.23526

lmY: 0.239194 +/- 0.235264

Arima: 0.2304 0.3281 0.7023 0.4825

@@

lmD: 0.1370797 +/- 0.1721383

lmY: 0.1371014 +/- 0.1721412

Arima: 0.1135 0.2908 0.3902 0.6964

@@

lmD: 0.02925782 +/- 0.02144818

lmY: 0.02925974 +/- 0.02144855

Arima: 0.0293 0.0223 1.3139 0.1889

@@

lmD: 6.254578 +/- 4.293245

lmY: 6.255019 +/- 4.293318

Arima: 6.2546 4.3752 1.4296 0.1528

@@

lmD: 0.0006000764 +/- 0.0003458892

lmY: 0.0006000719 +/- 0.0003458953

Arima: 6e-04 4e-04 1.5164 0.1294

@@

lmD: 0.0004422727 +/- 0.0002935454

lmY: 0.0004422599 +/- 0.0002935506

Arima: 4e-04 4e-04 1.2377 0.2158

@@

lmD: 0.008932077 +/- 0.005813607

lmY: 0.008932528 +/- 0.005813706

Arima: 0.0089 0.0061 1.4624 0.1436

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}

\begin{verbatim}
 Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
  <int>        <num>      <num>       <num>       <num>          <num>
\end{verbatim}

1: 13 225.5281 12.544463 242.3534 203.6571 227.4027
2: 315 183.2380 14.021218 205.7494 161.2362 183.4280
3: 393 211.4853 26.002452 254.6444 169.0380 210.8473
4: 501 259.8284 9.591647 272.2979 242.1095 260.8614
5: 591 227.3434 9.025312 240.3322 214.5732 225.0337
---\\
253: 65381 186.9246 8.529287 197.1196 173.4441 187.0577
254: 65423 194.8850 10.569185 207.5506 179.9910 196.8111
255: 65519 181.8946 11.823089 200.5545 165.3543 182.3613
256: 65529 178.3845 4.546207 186.4354 173.1996 176.4594
257: 65533 217.2415 16.147690 236.0007 182.0452 222.7584
wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
1: 2706.337 12 0.01659718 0.007597084 0.02543323 0.0041557214
2: 2931.808 16 0.01163209 0.008450614 0.02498250 0.0005249866
3: 6133.073 29 0.03494054 0.021369070 0.07259215 0.0044677582
4: 2598.284 10 0.01406600 0.008869984 0.02725920 0.0007449344
5: 3410.151 15 0.03288980 0.018031095 0.06712790 0.0011333915
---\\
253: 1682.321 9 0.03425477 0.010915540 0.05378668 0.0118438957
254: 2143.735 11 0.03947032 0.018939813 0.07284705 0.0123456804
255: 2364.630 13 0.01785069 0.010225149 0.04054656 0.0055296019
256: 1605.460 9 0.04394266 0.035577012 0.11668555 0.0112579853
257: 3693.105 17 0.04877689 0.033134593 0.09685661 0.0045080034
GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
1: 0.01721937 0.1991661 12 3.660370 1.651727
2: 0.01278289 0.1861135 16 1.988442 1.350952
3: 0.03071007 1.0132755 29 6.568530 3.245441
4: 0.01192006 0.1406600 10 3.555058 2.194372
5: 0.02545803 0.4933469 15 7.052047 3.532240
---\\
253: 0.03470823 0.3082929 9 6.159514 1.935746
254: 0.04550629 0.4341735 11 7.343593 3.465457
255: 0.01677883 0.2320589 13 3.108486 1.622229
256: 0.03000519 0.3954839 9 7.259927 5.518687
257: 0.04859240 0.8292071 17 9.892759 6.595347
GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
1: 5.649198 1.0029849 3.774258 43.92444 12 75.40653
2: 3.940819 0.1079590 2.312200 31.81508 16 76.61730
3: 11.440352 1.1326292 6.282210 190.48737 29 75.33588
4: 6.842022 0.2026931 3.093025 35.55058 10 74.03057
5: 13.497769 0.2712624 5.748451 105.78070 15 77.05677
---\\
253: 9.547676 2.2941778 6.272625 55.43563 9 77.12742
254: 13.894581 2.1950124 8.002303 80.77952 11 76.73931
255: 6.456701 1.0612959 2.882533 40.41032 13 76.78463
256: 18.438732 2.0755204 5.133219 65.33934 9 77.17689
257: 19.080014 1.0591174 10.403814 168.17691 17 75.18167
SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
1: 0.6667310 76.42244 74.38838 75.40725 904.8784 12 1993-05-13 04:33:30
2: 0.8567238 77.96388 75.26476 76.61909 1225.8768 16 1993-07-13 04:22:30
3: 1.5939261 77.95091 72.71007 75.33887 2184.7406 29 1993-08-12 04:45:30
4: 0.5362886 74.82883 73.23468 74.02978 740.3057 10 1993-10-04 14:30:30
5: 0.5907621 77.98809 76.13886 77.05264 1155.8515 15 1993-12-06 07:01:30
---\\
253: 0.4856759 77.83591 76.41717 77.12805 694.1468 9 2023-06-18 16:37:30
254: 0.5905545 77.62822 75.84766 76.74023 844.1324 11 2023-06-30 04:17:30
255: 0.7131983 77.88183 75.68429 76.78564 998.2002 13 2023-07-28 04:33:30
256: 0.5066369 77.91629 76.43632 77.17730 694.5920 9 2023-08-06 04:40:30
257: 0.9419447 76.67187 73.68745 75.18288 1278.0885 17 2023-08-06 16:04:30

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}

Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
1: 16423 249.6246 39.53847 315.8996 185.1393 248.8458
wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
1: 10484.23 42 0.03013706 0.02002665 0.07315483 0.000646732
GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
1: 0.02576315 1.265756 42 6.504293 3.430543
GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
1: 12.62058 0.2041703 6.416318 273.1803 42 74.25137
SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
1: 2.245081 77.98308 70.48178 74.26151 3118.558 42 2004-05-25 04:16:30
Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
1: 15087 228.4206 30.98628 279.3502 177.6686 229.0747
wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
1: 7081.037 31 0.01717012 0.01012086 0.03564823 0.0002394964
GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
1: 0.01952886 0.5322736 31 3.550457 1.75638
GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
1: 6.235319 0.065965 4.201192 110.0642 31 75.0963
SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
1: 1.712864 77.9228 72.27203 75.09567 2327.985 31 2003-09-05 05:06:30
{[}1{]} 3.550457

@@

\begin{verbatim}
2024-02-19 11:13:55.4 athan@tyler GHI_enh_04_investigate.R 0.693826 mins
\end{verbatim}
